### 2017-11-03 manuscript.rmd
fixed issues with ape::rotate

	species_tree = ape::read.tree( input_file_ml )
  species_tree = fix_names( species_tree )

@@

#Load tree
tree = species_ultrametric
tree$tip.label = str_replace_all(tree$tip.label,'_',' ')
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
ultratree <- chronos(tree)
class( ultratree ) = "phylo"

@@

```{r ultratree, echo=F, message=F, warning=F}
par(ask=F)
par(mfrow=c(1,1))
ultratree <- ape::rotate(ultratree, 31)
plotTree(ultratree, lwd = 4)

>>>>

	species_tree = ape::read.tree( input_file_ml )
  species_tree = fix_names( species_tree )
  species_tree_unladder =species_tree

@@

#Load tree
tree = species_tree_unladder
tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))
tree<-rotateNodes(tree,nodes=c(28,31))
ultratree <- chronos(tree)
class( ultratree ) = "phylo"

@@

```{r ultratree, echo=F, message=F, warning=F}
par(ask=F)
par(mfrow=c(1,1))
plotTree(ultratree, lwd = 4)
